Self Regulation Ontology Retest Analyses

### 2018-05-04 code/SRO_Retest_Analyses.Rmd
added closer look at diff score reliability

@@

```{r}
p1_t_legend <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='black')+
  theme(axis.text.y = element_text(size=43),
        legend.position = 'bottom',
        axis.text.x = element_text(size=23),
        axis.title.x = element_text(size=30), 
        legend.text = element_text(size=20), 
        legend.key.width = unit(0.75, "inches"), 
        legend.title = element_text(size=28),
        legend.spacing.x = unit(0.5, "inches")) + 
  guides(size = guide_legend(override.aes = list(size=c(9,18,28))),
         shape = guide_legend(override.aes = list(size=18)))+
  xlab("Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3), name="Type")+
  scale_size_continuous(name = "Sample Size")+
  geom_vline(xintercept = 0, color = "red", size = 1)

p1_t <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
  theme(axis.text.y = element_text(size=43),
        legend.position = 'none',
        axis.text.x = element_text(size=23),
        axis.title.x = element_text(size=30)) + 
  xlab("Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
  scale_size_continuous(range = c(5, 35))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p2_t <- lit_review %>%
  filter(task == 'survey') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#F8766D')+
  theme(axis.text.y = element_text(size=43),
        legend.position = 'none',
        axis.text.x = element_text(size=23),
        axis.title.x = element_text(size=30)) + 
  xlab("Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
  scale_size_continuous(range = c(5, 35))+
  geom_vline(xintercept = 0, color = "red", size = 1)

@@

```{r}
summary(lm(retest_reliability ~ task,rel_comp))
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            min_icc = min(icc),
            max_icc = max(icc),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc, -median_spearman)

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_spearman', 'median_icc',
                        'min_spearman', 'min_icc',
                        'max_spearman', 'max_icc'), digits=3)
```

@@

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            min_icc = min(icc),
            max_icc = max(icc),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc, -median_spearman)

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_spearman', 'median_icc',
                        'min_spearman', 'min_icc',
                        'max_spearman', 'max_icc'), digits=3)
```

@@

@@

test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/t1_data/meaningful_variables_clean.csv')
test_data$X <- as.character(test_data$X)
names(test_data)[which(names(test_data) == 'X')] <-'sub_id' 
retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/meaningful_variables_clean.csv')
retest_data$X <- as.character(retest_data$X)
names(retest_data)[which(names(retest_data) == 'X')] <-'sub_id'
retest_data = retest_data[retest_data$sub_id %in% test_data$sub_id,]
```

@@

```{r}
ggplotly(rel_df_mngfl %>%
  filter(grepl("logTr", dv)) %>%
  mutate(dv = gsub(".ReflogTr", "", dv),
         dv = gsub(".logTr", "", dv)) %>%
  left_join(rel_df[,c("dv", "icc")], by="dv") %>%
  ggplot(aes(icc.x, icc.y, color=task, label=dv))+
  geom_point()+
  theme_bw()+
  xlab("Reliability for transformed variable")+
  ylab("Reliability for raw variable")+
  geom_abline(slope=1, intercept=0),
  label=dv)
```

>>>>

summary(test_demog %>%
          select(Sex, Age))

@@

```{r}
p1_t_legend <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='black')+
  theme(axis.text.y = element_text(size=43),
        legend.position = 'bottom',
        axis.text.x = element_text(size=23),
        axis.title.x = element_text(size=30), 
        legend.text = element_text(size=20), 
        legend.key.width = unit(0.75, "inches"), 
        legend.title = element_text(size=28),
        legend.spacing.x = unit(0.5, "inches")) + 
  guides(size = guide_legend(override.aes = list(size=c(9,18,28))),
         shape = guide_legend(override.aes = list(size=18)))+
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3), name="Type")+
  scale_size_continuous(name = "Sample Size")+
  geom_vline(xintercept = 0, color = "red", size = 1)

p1_t <- lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
  theme(axis.text.y = element_text(size=43),
        legend.position = 'none',
        axis.text.x = element_text(size=23),
        axis.title.x = element_text(size=30)) + 
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
  scale_size_continuous(range = c(5, 35))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p2_t <- lit_review %>%
  filter(task == 'survey') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#F8766D')+
  theme(axis.text.y = element_text(size=43),
        legend.position = 'none',
        axis.text.x = element_text(size=23),
        axis.title.x = element_text(size=30)) + 
  xlab("Retest Reliability")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))+
  scale_size_continuous(range = c(5, 35))+
  geom_vline(xintercept = 0, color = "red", size = 1)

@@

```{r}
summary(rel_comp$sample_size[rel_comp$task == "survey"])
summary(rel_comp$sample_size[rel_comp$task == "task"])
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc, -median_spearman)

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_spearman', 'median_icc',
                        'min_spearman', 'icc_2.5',
                        'max_spearman', 'icc_97.5'), digits=3)
```

@@

"consistent with the summing of variance in the difference score"

```{r}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition",
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc", "var_subs","var_ind", "var_resid")], by = 'dv') %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid),
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid), 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)) %>%
  select(-task, -ddm_task, -num_all_trials, -var_resid, -var_subs, -var_ind) %>%
  gather(key, value, -dv, -overall_difference, -raw_fit, -rt_acc, -icc)

tmp %>%
  filter(key == "var_resid_pct") %>%
  ggplot(aes(raw_fit, value, fill=overall_difference))+
  geom_boxplot()

summary(lmer(value  ~ overall_difference*raw_fit + (1|dv), data=tmp %>% filter(key=="var_resid_pct")))

#Simple effects
summary(lmer(value  ~ overall_difference + (1|dv), data=tmp %>% filter(key=="var_resid_pct", raw_fit== "EZ")))

summary(lmer(value  ~ overall_difference + (1|dv), data=tmp %>% filter(key=="var_resid_pct", raw_fit== "raw")))

summary(lmer(value  ~ overall_difference + (1|dv), data=tmp %>% filter(key=="var_resid_pct", raw_fit== "hddm")))
```

Checking Rogosa's claim that ‘Difference scores are reliable when individual differences in true change exist.’
How do we measure ‘individual difference in true change’ 
1.between subject variability in difference score distributions
2.within subject variance in icc
Using 2 (because comparable between subject variance across different measures would be hard)
Expecting to see: positive correlation between mean icc and mean var_ind_pct
Result: The correlation between mean icc and mean var ind pct is NOT significant BUT looking at the distribution of mean var ind pct there is not a lot of variability t

```{r}
tmp = tmp %>%
  spread(key, value) %>%
  group_by(dv) %>%
  summarise(mean_var_ind_pct = mean(var_ind_pct),
            mean_var_subs_pct = mean(var_subs_pct),
            mean_icc = mean(icc)) %>%
  left_join(measure_labels, by='dv')

tmp %>%
  filter(overall_difference == 'difference') %>%
  ggplot(aes(mean_var_ind_pct, mean_icc))+
  geom_point()+
  geom_abline(slope=1, intercept=0)+
  geom_smooth(method = "lm")

summary(lm(mean_icc ~ mean_var_ind_pct,data=tmp %>%
  filter(overall_difference == 'difference')))

tmp %>%
  filter(overall_difference == 'difference') %>%
  ggplot(aes(mean_var_ind_pct))+
  geom_density()

summary(tmp$mean_var_ind_pct[tmp$overall_difference == "difference"])
summary(tmp$mean_var_subs_pct[tmp$overall_difference == "difference"])

tmp = tmp %>% filter(overall_difference == 'difference')
t.test(tmp$mean_var_ind_pct, tmp$mean_var_subs_pct, paired=T)
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc, -median_spearman)

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_spearman', 'median_icc',
                        'min_spearman', 'icc_2.5',
                        'max_spearman', 'icc_97.5'), digits=3)
```

@@

### Number of items

Does number of items in a survey have a significant effect on the average ICC of survey measures? No.

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
  left_join(boot_df[,c("dv", "spearman","icc")], by='dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

@@

test_data <- read.csv(paste0(retest_data_path,'t1_data/meaningful_variables_clean.csv'))
test_data$X <- as.character(test_data$X)
names(test_data)[which(names(test_data) == 'X')] <-'sub_id' 
retest_data <- read.csv(paste0(retest_data_path,'meaningful_variables_clean.csv'))
retest_data$X <- as.character(retest_data$X)
names(retest_data)[which(names(retest_data) == 'X')] <-'sub_id'
retest_data = retest_data[retest_data$sub_id %in% test_data$sub_id,]
```

@@

```{r warning=FALSE, message=FALSE}
ggplotly(rel_df_mngfl %>%
  filter(grepl("logTr", dv)) %>%
  mutate(dv = gsub(".ReflogTr", "", dv),
         dv = gsub(".logTr", "", dv)) %>%
  left_join(rel_df[,c("dv", "icc")], by="dv") %>%
  ggplot(aes(icc.x, icc.y, color=task, label=dv))+
  geom_point()+
  theme_bw()+
  xlab("Reliability for transformed variable")+
  ylab("Reliability for raw variable")+
  geom_abline(slope=1, intercept=0),
  label=dv)
```
